(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-11 ms.tex
references

\newcommand{\caltech}{2}
\newcommand{\cfa}{3}
\newcommand{\nyu}{4}
\newcommand{\princeton}{5}
\newcommand{\mpia}{6}
\newcommand{\cds}{7}
\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{1,\caltech,\cfa},
Daniel~Foreman-Mackey\altaffilmark{\nyu},
Timothy~D.~Morton\altaffilmark{\princeton},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler,
David~W.~Latham,
Allyson~Bieryla,
Andrew~W.~Mann,
And Any TRES Team Members We Should Add
}

\altaffiltext{1}         {btm@astro.caltech.edu}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}

@@

\keywords{\btmtodo{Keywords}}

@@

With the exception of one object, all of the stellar parameters are derived from comparing
photometric observations to the Dartmouth stellar evolution models.
As a result, both the stellar and planet parameters are subject to systematic biases induced
by discrepancies between the models and reality.

@@

B.T.M. is supported by the National Science Foundation Graduate Research
Fellowship under Grant No. DGE‐1144469.
J.A.J. is supported by generous grants from the David and Lucile Packard
Foundation and the Alfred P. Sloan Foundation.

D.F.M. and D.W.H. were partially supported by the National Science Foundation
(grant IIS-1124794), the National Aeronautics and Space Administration (grant
NNX12AI50G), and the Moore–Sloan Data Science Environment at NYU.

@@

{\it Facilities:} \facility{Kepler}%, \btmtodo{More...}

@@

\include{table_photometry}
\turnpage

@@

\include{table_fpp}

>>>>

\newcommand{\caltech}{1}
\newcommand{\cfa}{2}
\newcommand{\nyu}{3}
\newcommand{\princeton}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\jcpa}{7}
\newcommand{\texas}{8}
\newcommand{\hjs}{9}

\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
Daniel~Foreman-Mackey\altaffilmark{\nyu},
Timothy~D.~Morton\altaffilmark{\princeton},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler\altaffilmark{\caltech, \jcpa},
David~W.~Latham\altaffilmark{\cfa},
Allyson~Bieryla\altaffilmark{\cfa},
Andrew~W.~Mann\altaffilmark{\texas, \hjs},
And Any TRES Team Members We Should Add
}

\email{btm@astro.caltech.edu}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\jcpa} {Caltech Joint Center for Planetary Astronomy Fellow}
\altaffiltext{\texas} {Department of Astronomy, The University of Texas at
                            Austin, Austin, TX 78712, USA}
\altaffiltext{\hjs} {Harlan J. Smith Fellow, The University of Texas at Austin}

@@

\keywords{catalogs --- planetary systems --- planets and satellites: detection
                   --- stars: fundamental parameters}

@@

With the exception of one object, all of the stellar parameters are derived from comparing
photometric observations to the Dartmouth stellar evolution models.
As a result, both the stellar and planet parameters are subject to systematic biases induced
by discrepancies between the models and reality.
Even more dangerously, any region of parameter space not probed by the models would 
be entirely missed in our stellar modeling.

As stated in \textsection\ref{sec:stellarparams}, we place a distance upper limit of 500 pc 
for all stars in our sample. 
Given the location of the \Ci\ field with respect to the galactic plane, we expect a low 
contamination rate by halo giants. 
However, there are a few stars that are possibly miscategorized giants.
EPIC 201257461 is identified in the RAdial Velocity Experiment (RAVE) Fourth Data Release
as a target with $\logg = 3.18$, consistent with that of a giant star.
It is therefore perhaps not surprising that this system is flagged as a false positive based on 
the transit shape.

@@

B.T.M. is supported by the National Science Foundation Graduate Research
Fellowship under Grant No. DGE-€1144469.
J.A.J. is supported by generous grants from the David and Lucile Packard
Foundation and the Alfred P. Sloan Foundation.

D.F.M. and D.W.H. were partially supported by the National Science Foundation
(grant IIS-1124794), the National Aeronautics and Space Administration (grant
NNX12AI50G), and the Moore-Sloan Data Science Environment at NYU.

@@

{\it Facilities:} \facility{Kepler}, \btmtodo{More...}

@@

\include{table_photometry}
%\turnpage

@@

\include{table_planets}
\turnpage
\include{table_fpp}
